Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-07 main.tex
Add placeholder cooperation rate heatmaps.
Added without comment. These are for 20 repetitions. I've got 10k
repetitions coming down the pipes.

    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
    \label{fig:comparison_fingerprint_noisy}
\end{figure}

% TODO Include collaboration rating heatmaps

@@

    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
    \label{fig:comparison_fingerprint_noisy}
\end{figure}

% TODO Include collaboration rating heatmaps

>>>>

    \caption{Comparison of Fingerprints for Standard Tournament Top 3}
    \label{fig:comparison_fingerprint_standard}
\end{figure}
% TODO Add text ref to this

Figure~\ref{fig:comparison_cooperation_heatmaps_standard} shows the rate of
cooperation in each round for the top three strategies.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_EvolvedLookerUp2_2_2_array.pdf}
        \caption{Cooperation rate per round for EvolvedLookerUp\_2\_2\_2 (over
        20 repetitions)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_HMM_5_array.pdf}
        \caption{Cooperation rate per round for Evolved\_HMM\_5 (over 20
        repetitions)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_FSM_16_array.pdf}
        \caption{Cooperation rate per round for Evolved\_FSM\_16 (over 20
        repetitions)}
    \end{subfigure}%

    \caption{Comparison of collaboration rates for Standard Tournament Top 3}
    \label{fig:comparison_cooperation_heatmaps_standard}
\end{figure}

% TODO Update these with 10k repetition version

@@

    \caption{Comparison of Fingerprints for Noisy (5\%) Tournament Top 3}
    \label{fig:comparison_fingerprint_noisy}
\end{figure}
% TODO Add text ref to this

Figure~\ref{fig:comparison_cooperation_heatmaps_noisy} shows the rate of
cooperation in each round for the top three strategies.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_DBS_0-75_3_4_3_5_array.pdf}
        \caption{Cooperation rate per round for DBS (over 20 repetitions)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_ANN_5_Noise_05_array.pdf}
        \caption{Cooperation rate per round for Evolved\_ANN\_5\_Noise\_05 (over 20
        repetitions)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./assets/cooperation_0_0_20_Evolved_FSM_16_Noise_05_array.pdf}
        \caption{Cooperation rate per round for Evolved\_FSM\_16\_Noise\_05 (over 20
        repetitions)}
    \end{subfigure}%

    \caption{Comparison of collaboration rates for Noisy (5\%) Tournament Top 3}
    \label{fig:comparison_cooperation_heatmaps_noisy}
\end{figure}

% TODO Update these with 10k repetition version
